A Natural Language Processing Approach for the Digitalization of Roaming Agreement

### 2022-06-25 A_Natural_Language_Processing_Approach_for_the_Digitalization_of_Roaming_Agreements/sections/Results.tex
25.06.22

\section{Discussion of Results}\label{results}
Our NLP Engine architecture receives PDF files as inputs, and PDF files normally consist of unstructured text. Because of this, undesired characters may remain despite text parsing. Therefore, it is mandatory to determine the \textit{accuracy} of the results obtained once the output JSON file has been populated. For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results. On the one hand, a simple inspection at the sub-article level and on the other hand, a verification based on symbol comparison. The tests have been performed on two real RA samples from the mobile operators Proximus and Orange \cite{proximus}. Each experiment is described below and the results obtained are discussed in the same section.

>>>>

\section{Discussion of Results}\label{sec:results}
Our NLP Engine architecture receives PDF files as inputs, and PDF files normally consist of unstructured text. Because of this, undesired characters may remain despite text parsing. Therefore, it is mandatory to determine the \textit{accuracy} of the results obtained once the output JSON file has been populated. For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results. On the one hand, a simple inspection at the sub-article level and on the other hand, a verification based on symbol comparison. The tests have been performed on two real RA samples from the mobile operators Proximus and Orange \cite{proximus}. Each experiment is described below and the results obtained are discussed in the same section.
